Correlation Clustering with Dynamic Super-Nodes (DySNCC)

### 2014-10-09 paper/egpaper_for_review.tex
improved paper, and new autoScale option
permutation as option

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}
%%%%%%%%% TITLE
\include{my_macros.tex}
\title{Intersection Fusion Moves \\ Fusion Moves for Multicut Objectives}

@@

%------------------------------------------------------------------------
\section{Name of My Method (Union Fusion Cut)}

Global optimal solvers for multicut do not scale beyond ??? \cite{???}.
Good approximate solvers for planar graphs exist \cite{beifiger_2014_cvpr,yarkony_2012_eccv} 
but have difficulties to find good solutions for non planar graphs \cite{beier_2014_cvpr}.

>>>>

% Pages are numbered in submission mode, and unnumbered in camera-ready
\ifcvprfinal\pagestyle{empty}\fi
\begin{document}
%%%%%%%%% TITLE
\include{my_macros.tex}
\title{Correlation Clustering with Dynamic Super-Nodes (DySNCC)}

@@

\subsection{Karger-Stein Algorithms}
Use randomized procedure to reduce the number of nodes / edges to a reasonable 
number.
On the smaller graph, more expensive solvers are used.

%------------------------------------------------------------------------
\section{Intersection Fusion Cut}

Global optimal solvers for multicut do not scale beyond ??? \cite{???}.
Good approximate solvers for planar graphs exist \cite{beier_2014_cvpr,yarkony_2012_eccv} 
but have difficulties to find good solutions for non planar graphs \cite{beier_2014_cvpr}.
%
To make multicuts scalable, it is desirable to replace the graph $G$
with a graph $\hat{G}$, which is smaller in the number of nodes and edges. 
If $\hat{G}$ is small enough, it is feasible to use global optimal solvers.
%
A trivial way to reduce the size of the graph  is edge contraction.
Until a desirable size is reached, one might contract the edge with
the highest weight. A cut on the contracted graph  $\hat{G}$ is always
a valid cut on $\hat{G}$.
%
On the other hand, if an edge $e$ is contracted, it will never be cut.
If $e$ is part of the cut in a global optimal solution, we cannot find
this cut.
%
To overcome this problem  we can randomize the edge contraction,
and repeat this multiple times and remember the best solution.
%
But this would throw away all the ``not the best'' solutions (rewrite me).
Within this work we propose the following nifty trick.
Instead of throwing away solutions, we intersect them with the 
best solution, and solve the multicut on the resulting
graph.
Therefore we fuse multiple solutions,
